The State of Graph Processing \\ \large APIs, Libraries, Benchmarks, and Programming Languages \vspace{-1em}

### 2016-12-15 taxonomy/taxonomy.tex
Updated taxonomy and broke up into 5 sections.
Added a bit for dynamic graphs. The APIs and libraries
are definitely not complete, nor is the programming languages.
Next order of priority is to update programming languages.

\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in, headheight=15pt]{geometry}
\usepackage{amsmath, amsthm, amsfonts}
\usepackage{hyperref}
\usepackage{pgfplotstable, booktabs}
\pgfplotsset{compat=1.12}

@@

\begin{document}
\title{The State of Graph Processing \\ \large APIs, Libraries, Platforms, and Programming Languages \vspace{-1em}}
\author{Samuel Pollard}
\date{\today}
\maketitle

\section{APIs and Libraries}
\begin{itemize}
	\item \textbf{Pregel.} API; developed by Google; distributed; vertex centric, Bulk-Synchronous Parallel model; inspired many other platforms such as Giraph and GPS; \href{http://dl.acm.org/citation.cfm?id=1807184}{original paper}; 20.

@@

	\item \textbf{GraphX} Library.
\end{itemize}

\section{Programming Languages}

\section{Benchmarks}
\begin{itemize}
	\item \textbf{Graphalytics.} CPU and GPU; Supports GraphMat, GraphX, PowerGraph
	\item \textbf{GAP (Graph Algorithm Platform).} CPU; shared Memory (OpenMP); Berkeley; last active October 2016 on Github.
	\item \textbf{GraphBIG.} CPU and GPU; shared Memory and CUDA; last active February 2016.
	\item \textbf{Lonestar.} CPU and GPU; shared memory and CUDA; part of Galois. First appeared 2011; last update appears to be in 2015.
\end{itemize}
\section{Dynamic Graphs}
TODO: Determine if they are parallel or serial.
\begin{itemize}
	\item \textbf{STINGER.} Data structure and library; Georgia Institute of Technology and various national laboratories; streaming model; parallel or serial, distributed or shared; \href{http://cass-mt.pnnl.gov/docs/pubs/pnnlgeorgiatechsandiastinger-u.pdf}{original paper}; \href{http://www.stingergraph.com/}{website}; First appeared 2009; still active on Github.

	\item \textbf{DynoGraph.} \href{http://sc16.supercomputing.org/sc-archive/tech_poster/poster_files/post214s2-file3.pdf}{original paper}.

	\item \textbf{GraphJet.} \href{http://www.vldb.org/pvldb/vol9/p1281-sharma.pdf}{original paper}.

	\item \textbf{GraphStream.} Java library; I'm not sure but it appears to be serial; \href{https://arxiv.org/abs/0803.2093}{original paper}; first active 2007; appears still active;
\end{itemize}

@@

>>>>

\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in, headheight=15pt]{geometry}
\usepackage{amsmath, amsthm, amsfonts}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{pgfplotstable, booktabs}
\pgfplotsset{compat=1.12}

@@

\begin{document}
\title{The State of Graph Processing \\ \large APIs, Libraries, Benchmarks, and Programming Languages \vspace{-1em}}
\author{Samuel Pollard}
\date{\today}
\maketitle

\section{APIs and Libraries}
\begin{itemize}
	\item \textbf{Pregel.} API; developed by Google; distributed; vertex centric, Bulk-Synchronous Parallel model; inspired many other platforms such as Giraph and GPS; \href{http://dl.acm.org/citation.cfm?id=1807184}{original paper}; 2010.

@@

	\item \textbf{GraphX} Library.

	% OpenCL: http://www.lidi.info.unlp.edu.ar/WorldComp2011-Mirror/PDP3248.pdf - Appears inactive since 2011.
\end{itemize}

\section{Programming Languages}
\begin{itemize}
	\item \textbf{GP (Graph Programs).} Nondeterministic; serial; original paper: \cite{Plump:2009:GPL}; website: \url{https://www.cs.york.ac.uk/plasma/wiki/index.php?title=GP_(Graph_Programs)}; appears to be more theoretical and used for program verification; still active.

	\item \textbf{Gremlin.} functional, data flow; distributed; a way to interact with graph databases; \cite{Rodriguez:2015:Gremlin}; website: \url{http://tinkerpop.apache.org/gremlin.html}.
\end{itemize}

\section{Benchmarks}
\begin{itemize}
	\item \textbf{Graphalytics.} CPU and GPU; supports GraphMat, PowerGraph, GraphBIG, Giraph, GraphX, Neo4j, and MapReduce; \cite{Capota:2015:Graphalytics}; still active; so far I can only get PowerGraph and GraphBIG running; website: \url{http://graphalytics.ewi.tudelft.nl}.

	\item \textbf{GAP (Graph Algorithm Platform).} CPU; shared Memory (OpenMP); \url{http://gap.cs.berkeley.edu/benchmark.html}; last active October 2016 on Github. \cite{Beamer:2015:GAPBench}

	\item \textbf{GraphBIG.} CPU and GPU; shared Memory and CUDA; last active February 2016.

	\item \textbf{Lonestar.} CPU and GPU; shared memory and CUDA; part of Galois. First appeared 2011; last update appears to be in 2015 though I am in recent (December 2016) contact with someone working on the project.
\end{itemize}

\section{Dynamic Graphs}
\begin{itemize}
	\item \textbf{STINGER.} Data structure and library; Georgia Institute of Technology and various national laboratories; streaming model; parallel or serial, distributed or shared; \href{http://cass-mt.pnnl.gov/docs/pubs/pnnlgeorgiatechsandiastinger-u.pdf}{original paper}; \href{http://www.stingergraph.com/}{website}; First appeared 2009; still active on Github.

	\item \textbf{GraphJet.} Java library; parallel but single-machine; original purpose was for real time recommendations from Twitter; \url{https://github.com/twitter/GraphJet}; \cite{Sharma:2016:GraphJet}.

	\item \textbf{GraphStream.} Java library; I'm not sure but it appears to be serial; \url{http://graphstream-project.org/}; \cite{Dutot:2007:GraphStream} first active 2007; appears still active.

	\item \textbf{Kineograph.} API; parallel and distributed; \cite{Cheng:2012:Kineograph}; 2012; appears to be inactive but influenced GraphX, GraphChi, and PowerGraph.

	\item \textbf{DynoGraph.} Performance Analysis; \url{https://github.com/sirpoovey/DynoGraph} \cite{Hein:2016:DynoGraph}; connected components, PageRank, BFS; right now just a repo and a poster at SC'16.
\end{itemize}

@@

% Other stuff: Giraph++: http://dl.acm.org/citation.cfm?id=2732238
% GraphBuilder: http://dl.acm.org/citation.cfm?id=2484429 and https://01.org/graphbuilder/ - Active from 2013--2014
% Chronos: http://dl.acm.org/citation.cfm?id=2592799
% X-Stream: http://dl.acm.org/citation.cfm?id=2522740

\bibliographystyle{plain}
\bibliography{../report/drp}
